Towards a classification framework for social machines

### 2013-02-24 latex/paper_new.tex
working on 4.3

\begin{table}[htb]
\begin{center}
\begin{tabular}{|p{8cm}|}
\hline
{\bf Users and Roles} \\
\hline
Generality of Audience \\
Participant autonomy \\
Participant anonymity \\
Extent of hierarchical organisation of roles \\
Clear separation of roles/responsibilities among participants \\
\hline
{\bf Tasks} \\
\hline
Task involves creative production or creation of content \\
Task involves subjective appraisal of content \\
Task solves (a defnable) computation problem/set of problems\\
Domain-specificity of tasks \\
Service/platform derives benefit from participation \\
Variation in types of contributions and tasks \\
\hline
{\bf Motivation} \\
\hline
Participants are intrinsically motivated:\\
\hspace{1cm} to gain/share knowledge \\
\hspace{1cm} to ``get something done'' \\
\hspace{1cm} to ``for fun/entertainment''\\
\hspace{1cm} to ``be social'' \\
Participation is motivated by extrinsic reward (payment, status etc) \\
Participation is done for the benefit of a specific third-party \\
Participation is done for the benefit of society as a whole \\
\hline
{\bf Context of Participation} \\
\hline
Participants' (geographic) location is relevant to the service \\
Participation is done via: \\
\hspace{1cm} mobile devices \\
\hspace{1cm} web browsers \\
\hspace{1cm} apps \\
\hspace{1cm} sensors/sensing (location sensing and wearable devices) \\
Participation is done in a mobile context \\
\hline
\end{tabular}
\end{center}
\caption{Consolidated constructs of social machines.} \label{table:constructs}
\end{table}

@@

\subsubsection{Tasks, Problems and Activiites}
The first set of constructs pertain to \emph{what} the participants do
individually and collectively within the system.  This task could
involve creation of content, subjective appraisal of content, posing
of problems, group solving of problems, and so on.  Tasks relate to a
pre-defined problem space or domain, or may be support a general,
broad collection of activities.  Finally, a question of whether a
direct benefit is derived by the platform/machine provider other than
the benefits gained by participants through participation.

>>>>

\begin{table}[htb]
\begin{center}
\begin{tabular}{|p{8cm}|}
\hline
{\bf Users and Roles} \\
\hline
Generality of Audience \\
Participant autonomy \\
Participant anonymity \\
Extent of hierarchical organisation of roles \\
Clear separation of roles/responsibilities among participants \\
\hline
{\bf Tasks} \\
\hline
Activities involve creative production of content \\
Activities involve subjective appraisal of content \\
Activities involve solving (a definable) computation task or set of problems\\
Tasks are domain-specific \\
The machine owner (service/platform) derives benefit from participation \\
Activities and tasks are pre-defined or participant-defined \\
Variation in types of contributions and tasks \\
\hline
{\bf Motivation} \\
\hline
Participants are intrinsically motivated:\\
\hspace{1cm} to gain/share knowledge \\
\hspace{1cm} to ``get something done'' \\
\hspace{1cm} to ``for fun/entertainment''\\
\hspace{1cm} to ``be social'' \\
\hspace{1cm} for the benefit of a specific group of people who need help \\ 
\hspace{1cm} for the benefit of society as a whole \\ 
Participation is motivated by extrinsic reward (payment, status etc) \\
\hline
{\bf Context of Participation} \\
\hline
Participants' participate to fulfill needs of a role  \\
\hspace{1cm} work-related/professional role
\hspace{1cm} home/family related
\hspace{1cm} social role
\hspace{1cm} leisure/entertainment role
Participants' physical location is relevant to the service \\
Participation is done via: \\
\hspace{1cm} mobile devices \\
\hspace{1cm} web browsers \\
\hspace{1cm} apps \\
\hspace{1cm} sensors/sensing (location sensing and wearable devices) \\
Participation is done in a mobile context \\
\hline
\end{tabular}
\end{center}
\caption{Consolidated constructs of social machines.} \label{table:constructs}
\end{table}

@@

\subsubsection{Tasks, Problems and Activiites}
The first set of constructs pertain to \emph{what} the participants
do, both individually within the system, and collectively as a whole.
Individual activities might include creation of content, subjective
appraisal of existing content, posing of problems, solving of
problems, andf so on.  The resulting computation, looked at from a
macroscopic whole, might be the identification of high-quality
artistic content, insight, or creative works, collective problem
solving, and so on.  Such tasks might be pre-defined by the system
designers, or brought to the system by participants.  Futher, these
tasks might be of a specific type or class, or of many varied types or
encompass a general class of activities.  To capture these
difeferences, we include a construct that differentiates machines with
pre-defined problem spaces or are open to participant-provided tasks
and activities.  Finally, we ask whether the benefit derived by
participants is distinct from that gained by machine/platform owners
and service providers.

\subsubsection{Motivation}
The third set of themes pertains to the motivation that sustains
continued participation in these systems.  We identiy 6 different
kinds of common sources of intrinsic motivation; first, that
participation is fun, second that it accomplishes an activity that the
participant enjoys or wanted to get done, third, that it satisfies the
desire to gain or share knowledge, or, fourth, or to be social.  The
last two pertain to philanthropy, whether participation is seen to
benefit a particular group of disadvantaged people or individuals who
need assistance, or, finally, if participation is beneficial to
society as a whole.  Finally, we ask whether extrinsic motivational
factors also contributed to sustained participation - such factors
could include money reward, status, recognition and so on

\subsection{Context of Participation}
The final set of constructs pertains to the context(s) of each
participant's greater (life-) activities that participation is
performed.  This context could be in a work context, home/family
context, for leisure, and at a desk or away from a computer (in a
mobile context).  PArticipation could be conducted via apps, web
browsers, sensors and other technolgoies.  Due to the predominance of
``geo-locative'' services that incorporate information about the
user's location, we have included a construct identifying the degree
to which the user's location is used by the machine.
